Microlensing as a possible probe of the internal structure of quasars

### 2015-07-12 paper1/fitting.tex
fitting.tex small corrections

\begin{figure}
\centering
\includegraphics[width=0.9\hsize%,bb=0 0 576 432
                ]{plots/data_cc.eps}
\includegraphics[width=0.9\hsize%,bb=0 0 576 432
                ]{plots/data_dd.eps}
\includegraphics[width=0.9\hsize%,bb=0 0 576 432
                ]{plots/data_gg.eps}
\caption{\label{fig:mockdata} Three different mock datasets with
  three different parameterisations fitted to each --- crescent (red),
  uniform-disk (blue) and Gaussian disk (green).}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=0.9\hsize%,bb=0 0 576 432
                  ]{plots/Rp4all.eps}
\caption{\label{fig:mcmc} Posterior probability distribution for the
  source size $R_p$.  The vertical line is the correct value. Same
  color represeents the same dataset whereas same line style
  corresponds to same model fit.  The legend gives the reduced
  $\chi^2$ of the best fit in each case.}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.9\hsize%,bb=0 0 576 432
                ]{plots/data_cc.eps}
\includegraphics[width=0.9\hsize%,bb=0 0 576 432
                ]{plots/data_dd.eps}
\includegraphics[width=0.9\hsize%,bb=0 0 576 432
                ]{plots/data_gg.eps}
\caption{\label{fig:mockdata} Three different mock datasets with
  three different parametrisations fitted to each --- crescent (red),
  uniform-disk (blue) and Gaussian disk (green).}
\end{figure}

@@

\begin{figure}
\centering
  \includegraphics[width=0.9\hsize%,bb=0 0 576 432
                  ]{plots/Rp4all.eps}
\caption{\label{fig:mcmc} Posterior probability distribution for the
  source size $R_p$.  The vertical line is the correct value. Same
  color represents the same dataset whereas same line style
  corresponds to same model fit.  The legend gives the reduced
  $\chi^2$ of the best fit in each case.}
\end{figure}
